---
title: "DSCI401 Homework 1"
author: "Lauren Wehausen"
date: "9/1/2022"
output: html_document
---
Q2
cubs <- read.csv("https://raw.githubusercontent.com/gjm112/DSCI401/main/data/cubs_all_time.csv")

2a. How many total games have the Cubs won and lost between 1876 and 2022?

```{r}
sum(cubs$W)
sum(cubs$L)
```
Total games won: 11141
Total games lost: 10592

2b. What year did the Cubs score the most runs? What year did the Cubs score the fewest runs? Do you have any thoughts about the year that the Cubs scored the fewest runs?

```{r}
cubs$Year[which.max(cubs$R)]
cubs$Year[which.min(cubs$R)]
```
Most: Cubs had the most runs, 1056, in 1894.
Least: Cubs had the least runs, 265, in 2020. 
This year was probably the worst because it was when COVID first began. Other than that, they just played a terrible season. 

2c. In how many seasons was the Cubs total attendance (i.e. the variable
Attendance) over 3 million?

```{r}
attend2 <- cubs$Attendance[!is.na(cubs$Attendance)] 
sum(attend2 > 3000000)
```

There were 12 seasons where the attendance was greater than 3,000,000.. 

3 and 4 are in my google colab, here is the link:
https://colab.research.google.com/drive/10IDQwO-CmSqpYQrtkTaqGqeL7c61RCTM

Please note: I have notes and projects/assignments from my undergrad python class (COMP180) which I used to answer question 4. I can show you this stuff on Tuesday if you would like proof of this :) 
